Examination of test statistics and p-values

### 2024-06-04 misc/pval_dist.Rmd
make p smaller

l <- lapply(0:80, function(x) {
  tulip <- c(200+x, 200-x)
  res <- chisq.test(tulip, p = c(1/2, 1/2))
  c("stat"=res$stat,"p"=res$p.value)
})

@@

>>>>

l <- lapply(0:150, function(x) {
  tulip <- c(200+x, 200-x)
  res <- chisq.test(tulip, p = c(1/2, 1/2))
  c("stat"=res$stat,"p"=res$p.value)
})

@@

## 20% window

This is the range we will use for determining the similarity of p-values.

The below table will be used to judge whether the p-values are reproducible.
